Relationship between solar wind, $D_{st}$, and plasmasphere mass density on one-hour time scales

### 2015-06-05 paper.tex
Data Preparation Edits

\section{Data}

For solar wind data, we use the \cite{Reconstruction}, which has a time coverage of 1972-2013.

Mass density data are from \cite{Denton}, which has a time coverage of 1980-1991 and is on a 15-minute time grid with many gaps.  A mean interpolation method was used to one-hour grid of the solar wind averages.  GIVE MORE DETAILS ABOUT THIS.  NEED ENOUGH INFORMATION TO BE ABLE TO REPRODUCE RESULTS GIVEN ONLY TWO DATA SETS.

Figure~\label{AllData} shows values of solar wind averages and mass density used in this study.

@@

We will briefly compare our results to other published results to verify our methods and handling of data.

@@

\begin{figure}[htp!]
\centering
(a)
\includegraphics[scale=0.7]{paperfigures/stormavs-dst.png}
(b)
\includegraphics[scale=0.7]{paperfigures/stormavs-mass.png}
\caption{(a) Average of solar wind and near-Earth measurements around the time D_${st}$ crossed below -40~nT onset. (b) Same as (a) except around time intervals where mass density crossed above $40 amu/cm^3$.  The bottom panel shows the number of mass density data points that were used for the average.}
\label{MassStorm}
\end{figure}
\clearpage

>>>>

\section{Data Preparation}

The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the data associated with \cite{Denton}, with data available from 1980-1991; all other variables are from \cite{Reconstruction} over the time range of 1972-2013, which are on a 1-hour time grid.  In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time, the value from GOES 7 was selected to avoid overlapping data points.  $\rho_{eq}$ is the inferred mass density based on the 3rd harmonic frequency of magnetic field measurements.  The smallest cadence for $\rho_{eq}$ values is 10 minutes.  To compute an hourly average over the same time range as the solar wind parameters, the median of all values in a given hourly range was used.  Fill values were used for hours when no measurements were available.

In this work events are considered when $D_{st}$ or $\rho_{eq}$ crosses a threshold value.  In finding events, all fill values were replaced with linearly interpolated values.  
% unless the gap was larger than X hours?

% Though this may skew the onset time slightly, it's thought to be less skewed than trying to determine start and end times with the NaNs in place. This interpolation was only used for determining storm times, and not for any analysis.
% If you say this, you need to do an experiement.  A review will say ``seems like it is an easy statement to check.  Why didn't you?''

% http://www.dartmouth.edu/~rdenton/Data/DentonTakahashiGOES1980-1991MassDensityWithHeader.txt
% This looks like a 10 minute grid, not 15 minute?

@@

Figure \ref{AllData} shows values of solar wind averages and mass density used in this study. We will briefly compare our results to other published results to verify our methods and handling of data.

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.5]{paperfigures/stormavs-dst.eps}
\includegraphics[scale=0.5]{paperfigures/stormavs-mass.eps}
\caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below -40~nT onset. (b) Same as (a) except around time intervals where mass density crossed above $40 amu/cm^3$.  The bottom panel shows the number of mass density data points that were used for the average.}
\label{MassStorm}
\end{figure}
\clearpage
